Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-15 paper.tex
pdf update as well

With the increase of deployed reactors, the number of batches of \glspl{PWR}
fuel loaded converges to the references one (a random cycle length
values if randomly determined for each deployed reactors), reducing its impact
on the uncertainty on the total uranium consumption.
The fuel enrichment contribution follow a close to constant uncertainty
contribution of $2\%$, so as the total relative uncertainty decrease, its
relative contribution increases over time.

>>>>

With the increase of deployed reactors, the number of batches of \glspl{LWR}
fuel loaded converges to the references one (a random cycle length
values if randomly determined for each deployed reactors), reducing its impact
on the uncertainty on the total uranium consumption.
The fuel enrichment contribution follow a close to constant uncertainty
contribution of $2\%$, so as the total relative uncertainty decrease, its
relative contribution increases over time.
